---
title: "Project Poster"
author: "Steven Hwang"
date: "March 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(MASS)
library(ggmap)
library(ggplot2)
library(dplyr)
library(faraway)
df.data <- read.csv(file='D:\\Program File\\Git\\git_projects\\STATS 504\\ProjectProposal\\stat-504-airbnb\\data\\listings.csv',header=TRUE,sep=',',stringsAsFactors=FALSE)

#Reducing to variables of interests
df.map <- dplyr::select(df.data, longitude, latitude, price)
df.data <- dplyr::select(df.data, price, host_is_superhost, host_has_profile_pic, host_identity_verified, 
                         neighbourhood_cleansed, property_type, room_type, accommodates, bathrooms, bedrooms, beds, bed_type, amenities, guests_included, minimum_nights, number_of_reviews)

#clean data
df.data$price <- as.numeric(gsub(",", "", substring(df.data$price,2)))
nrow(df.data)  # 13849

df.data <- df.data[!df.data$host_is_superhost == "",]
nrow(df.data)  # 13813

df.data$host_is_superhost <- factor(df.data$host_is_superhost)
df.data <- df.data[!df.data$host_has_profile_pic=="",]
nrow(df.data) #13813

df.data$host_has_profile_pic <- factor(df.data$host_has_profile_pic)
df.data <- df.data[!df.data$host_identity_verified=="",]
nrow(df.data) #13813

df.data$host_identity_verified <- factor(df.data$host_identity_verified)
df.data = df.data[!df.data$neighbourhood_cleansed == "",]
nrow(df.data)  # 13813

df.data$neighbourhood_cleansed <- factor(df.data$neighbourhood_cleansed)
df.data = df.data[!df.data$property_type == "",]
nrow(df.data)  # 13813

df.data$property_type <- factor(df.data$property_type)

df.data = df.data[!df.data$room_type == "",]
nrow(df.data)  # 13813
df.data$room_type <- factor(df.data$room_type)

df.data = df.data[!df.data$bed_type == "",]
nrow(df.data)  # 13813
df.data$bed_type <- factor(df.data$bed_type)

#Aemnities extraction
#Wireless Internet
df.data$wifi <- 'f'
df.data$wifi[grep("Wireless Internet", df.data$amenities, ignore.case = TRUE)] <- 't'
df.data$wifi <- factor(df.data$wifi)
#Free Parking on Premises
df.data$parking <- 'f'
df.data$parking[grep("Free Parking on Premises", df.data$amenities, ignore.case = TRUE)] <- 't'
df.data$parking <- factor(df.data$parking)
#Smoking Allowed
df.data$smoke <- 'f'
df.data$smoke[grep("Smoking Allowed", df.data$amenities, ignore.case = TRUE)] <- 't'
df.data$smoke <- factor(df.data$smoke)

#Drop amenities
df.data <- dplyr::select(df.data, -amenities)

# Remove data with null values
for (var in names(df.data)) {
  df.data = df.data[!is.na(df.data[,var]),]
}
nrow(df.data)  # 13767

sum(df.data$number_of_reviews == 0)  # 2451
# Listings with no reviews have few stays; their prices may not be indicitive of what they are worth.
df.data = df.data[!df.data$number_of_reviews == 0,]
nrow(df.data)  # 11316
#Drop number of reviews
df.data <- dplyr::select(df.data, -number_of_reviews)

summary(df.data$property_type)
# These types have less than 5 counts
property_types_to_remove = c(
  "Bungalow", "Chalet", "Earth House", "Dorm", "Hut", "Tent", "Yurt"
)
df.data = df.data[!df.data$property_type %in% property_types_to_remove,]
nrow(df.data)  # 11304

# Remove listings with accommodates outliers. 
df.data <- subset(df.data, !(accommodates > 10 & price < 150))
nrow(df.data)  # 11295

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Travelers are increasingly using short term vacation rentals as an alternative to traditional hotels for accomodations. The most popular service for short term vacation rentals is Airbnb, a website that lets anybody rent out their room, apartment, or house. Airbnb's popularity has created a potential revenue source for property owners. Homeowners with a spare bedroom now have the option to rent it out on their desired timeline. Apartment building owners now have the option to rent units to travelers instead of long term tenants. Central to the decision to become an Airbnb host is the expected revenue. Individuals will only list their properties on Airbnb if they expect to make above a certain amount of money. A model that predicts the rental price of a unit given its attributes can help potential Airbnb hosts decide whether to rent out their unit. The decision to host, however, is more complicated. Hosts have many choices about how to set up their short term vacation rental unit, and each choice may influence the price they can charge. Using Airbnb data from Amdsterdam, we model how the attributes a host can and cannot control about their Airbnb unit influence the amount they charge. Analysis and Interpretation of the model can help future Airbnb hosts anticipate potential revenue and determine the optimal way to set up their short term vacation rental unit.

## Background
* The data for this study was obtained from *insideairbnb* for active listings on 7/4/2016 in Amsterdam, Netherlands. 
* The data was reduced to 15 variables of interest for 13849 different listings on Airbnb.com.

| Variables         |Type             |Description                                          |
|-------------------|-----------------|-----------------------------------------------------|
| Price per night   | Account Setting | The price per night of the listing.                 |
| Host is superhost | Account Setting | Is the host an Airbnb superhost.                    | 
| Room type         | Account Setting | The room type of the listing (whole place or room). | 
| Accomodates       | Account Setting | The number of people the listing accomodates.       | 
| Profile picture   | Account Setting | Does the host has a profile picture.                |
| Identity verified | Account Setting | Is the hosts identity verified by Airbnb.           |  
| Guest included    | Account Setting | The number of guests included in the price.         | 
| Minimum nights    | Account Setting | Minimum booking nights.                             | 
| Amenities         | Account Setting | Type of amenities included.                         |
| Beds              | Control         | The number of beds.                                 | 
| Bed type          | Control         | The type of beds in the listing.                    |
| Neighbourhood     | Control         | Neighbourhood the listing is located in.            | 
| Property type     | Control         | The property type of the listing.                   | 
| Bathrooms         | Control         | The number of bathrooms.                            | 
| Bedrooms          | Control         | The number of bedrooms.                             | 

```{r map, echo=FALSE}
AmsterdamMap <- qmap('amsterdam', zoom = 12)
AmsterdamMap +
  stat_density2d(aes(x = longitude, y = latitude, fill=..level.., alpha=..level..), 
            data = df.map, geom='polygon', na.rm=TRUE) +
  scale_alpha_continuous(range=c(0.1,0.5), guide=FALSE) + ggtitle("A map of the density of Airbnb listings in Amsterdam") +
  guides(fill=guide_legend(title="Number of listings"))

```

## Methodology & Analysis

```{r,include=F}

```

After some data cleaing, we intend to bulid a regression model to predict house price. Our data frame has 17 varialbes. The first is responce and the others are predictors.

```{r,include=F}
summary(df.data)
```

We bulit an original regression model including all predictors and all samples. The residual plot shows there exist some outliers and variance of residuals are not constant. The QQ plot shows our data are not from normal distribution which has no effect on the basis of estimators but influences the tests of significance. Since our rule is to guarantee the high accuracy of prediction, we don't have to pay much attention on the non-normality. 

```{r,echo=F}
reg1=lm(price~.,data=df.data)
par(mfrow=c(2,2))
plot(reg1)
```

In order to solve the nonconstant variance problem, we should transform our response by using Boxcox. We can choose $\lambda=0$ and transform 'price' into 'log(price)'. Then, we remove outliers based on cook distance and standardized residual.After that, the residual plot shows the variance becomes constant.

```{r,include=F}
cook=cooks.distance(reg1)
halfnorm(cook) # 487, 5703
# 487 is removed because it only has 0.11 removed per month and costs $1307 per night.
# 5703 is removed because it has a minimum_nights value of 1000
bad_ids = c(487, 5703)
df.data = df.data[-bad_ids,]

# Remove points with minimum_nights > 15. These dont fall under the category of short term vacation
# rental. 
df.data = df.data[df.data$minimum_nights <= 15,]
nrow(df.data)  # 11223

reg <- lm(price~., data=df.data)
cook = cooks.distance(reg)
halfnorm(cook) # 100, 595
# 100 seems normal, but cheap.
# 595 sems normal but more expensive. Stop here
```

```{r,echo=F,fig.height=3}
boxcox(reg1,lambda = seq(-0.5,0.5,0.01))
```

```{r,echo=F}
lm.airbnb=lm(log(price)~.,data=df.data)
par(mfrow=c(2,2))
plot(lm.airbnb)
```

After outliers detection and response transformation, we can bulid a regression model with imporved data. Then we should select some variables which can maxmize the prediction accuracy. Cross validation is a proper approach to achieve this goal. We set the minimum variable number to be 10. Based on the result of our cross validation, we keep 'host_identity_verified','Host_has_profile_pic','Host_is_superhost',
'Neighbourhood_cleansed','Property_type','Room_type','Accommodates','Bathrooms','Bed_type','Wifi','parking' 10 varialbes. Below is the result of our regression model.


```{r,eval=F,echo=F}
ind=sample(1:11223,7656)
df.train=df.data[ind,]
df.test=df.data[-ind,]

num=0
for(i in 10:16){
  num=choose(16,i)+num
}
var.mat=matrix(c(0),nrow = num,ncol=16)
num=1
for(i in 10:16){
  commat=combn(16,i)
  for(j in 1: choose(16,i)){
    var.mat[num,commat[,j]]=rep(1,i)
    num=num+1
  }
}
score=rep(0,dim(var.mat)[1])
for(i in 1:dim(var.mat)[1]){
  l1=lm(log(price)~.,data=df.train[,c(TRUE,var.mat[i,]==1)])
  pred=predict.lm(l1,newdata = df.test)
  score[i]=sqrt(mean((df.test$price-exp(pred))^2))
}

```

```{r,echo=F,warning=F,message=F}
df.name=c('price','host_identity_verified','host_has_profile_pic','host_is_superhost',
'neighbourhood_cleansed','property_type','room_type','accommodates','bathrooms','bed_type','wifi','parking' )
lm.airbnb=lm(log(price)~.,data=df.data[,df.name])
```



## Results
The expected change in log of y with respect to a one-unit increase in x1 holding all other variables at any fixed value

* The results show that most airbnb account settings are significant at the 0.05 level except for bed types and parking. 
* The variable that had the strongest effect on the price per night is renting out the entire property. This increased the price per night by 2.24 times on average when compared to renting out a shared room while controlling for others.
* An interesting conclusion found was that smoking did not seem to have an affect on the price per night as the coeffecient is close to 1.

|                          |$\beta$   |exp($\beta$)    | SE    | p-value  |
|-------------------------|--------|--------------|-------|----------|
| Intercept               | 2.680  | 14.59       | 0.092 | < 2e-16  |
| Host is superhost       | 0.070  | 1.07        | 0.009 | 4.86e-14 |
| Room type: Private      | 0.397  | 1.49        | 0.008 | < 2e-16  |
| Room type: Entire Place | 0.806  | 2.24        | 0.045 | < 2e-16  |
| Accomodates             | 0.076  | 1.08        | 0.004 | < 2e-16  |
| # of Beds               | 0.006  | 1.01        | 0.004 | 0.0984   |
| Bed type: Couch         | 0.184  | 1.20        | 0.112 | 0.0997   |
| Bed type: Real Bed      | 0.076  | 1.08        | 0.076 | 0.1208   |
| Guest included          | 0.015  | 1.02        | 0.003 | 5.75e-07 |
| Minimum nights          | -0.019 | 0.98        | 0.002 | < 2e-16  |
| Wifi                    | 0.137  | 1.14        | 0.020 | 2.52e-12 |
| Parking                 | 0.019  | 1.02        | 0.013 | 0.1415   |
| Smoking                 | -0.024 | 0.98        | 0.009 | 0.0109   |

## Discussion
Given the attributes of an Airbnb unit, we are able to accurately predict the price per night with a $() root mean square error rate on a validation set. Our model is useful in useful in guiding hosts set up their unit; superhost, room type, accomodates, guests included, minimum nights, wifi, and smoking are all significant variables in our model at the 95% confidence level. The model shows the following: 

Becoming a superhost increases the average price per night by seven percent; hosts should attempt to fulfill the requirements of a superhost. As compared to a shared space, a private room raises the price per night by 50%, and an entire place raises the price 120%; depending on the property, this information can be used to optimize the configuration of an Airbnb rental. Each additional person a unit accommodates raises the price by 7.8% on average, so high density units may be worthwhile. Hosts that require a minimum number of nights charge less for their units, so if the work between stays is minimal, the model suggestions that hosts should not impose a minimum nights requirement. Units with wifi charge around 15% more on average; this information can be used by hosts to decide whether to purchase wifi for their unit. Lastly, units that allow smoking charge less per night, so the model does not indicate that hosts should allow this. 

It must be noted that this analysis does not imply that these attributes are the direct cause on price, as the model is based on observational data, not a randomized experiment. Nonetheless, the coefficients of the model provide useful indications for how hosts should set up their Airbnb units. The model can be improved with more data from locations other than Amsterdam, and more variables of rental units. Interaction effects should be considered, as well as nonlinear models. Regardless, a useful model was produced that provides useful insight into Airbnb vacation rentals.